prolfqua - R-package for Analysing Proteomics Label Free Quantification Experiments

### 2022-02-10 inst/MyArticle/MergePoster.Rmd
fix vignette

ttt <- sapply(allBenchmarks, function(x){x$complete(FALSE)})
res <- purrr::map_df(allBenchmarks, function(x){x$pAUC()})
res <- res |> dplyr::mutate(whatfix = case_when(what == "scaled.beta.based.significance" ~ "scaled.p.value", TRUE ~ what))

>>>>

ttt <- sapply(allBenchmarks, function(x){x$complete(FALSE)})
names(allBenchmarks)

b1 <- allBenchmarks$benchmark_imputation$pAUC
b1$get_confusion_benchmark

allBenchmarks[[1]]$pAUC

res <- purrr::map_df(allBenchmarks, function(x){x$pAUC()})
res <- res |> dplyr::mutate(whatfix = case_when(what == "scaled.beta.based.significance" ~ "scaled.p.value", TRUE ~ what))
